CF Registry Analysis

### 2022-12-11 Christine Chan/CF Registry/cf_registry_analysis.Rmd
mutations added

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(knitr)
library(parallel)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = "/home/tim/UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Laura/Peds Endo/Christine Chan/CF registry data")
```

@@

@@

>>>>

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(knitr)
library(parallel)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = "~/UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Laura/Peds Endo/Christine Chan/CF registry data")
```

@@

geno = read.csv("Data_Clean/genotypes.csv",header = F)

@@

# Genotypes
df$Mutation1 = factor(df$Mutation1,levels = geno[geno$V1=="mutation1","V2"],
                      labels = geno[geno$V1=="mutation1","V3"])
df$Mutation2 = factor(df$Mutation2,levels = geno[geno$V1=="mutation2","V2"],
                      labels = geno[geno$V1=="mutation2","V3"])
